Developing Measures of Public Perceptions of Values in Science

### 2022-05-17 talk/talk.qmd
talk to GH pages

---
title: "Developing Measures of Public Perceptions of Values in Science"
author: |
    | Dan Hicks 
    | Emilio Lobato
    | University of California, Merced
    | [`bit.ly/3w1RJSA`](https://bit.ly/3w1RJSA)
toc: false
toc-title: "Overview"
format: 
    revealjs:
        toc-depth: 1
        slide-number: true
        self-contained: true
        theme: [default, theming.scss]
link-citations: true
bibliography: ../paper/VISS.yaml
---

@@

[`bit.ly/3w1RJSA`](https://bit.ly/3w1RJSA)

>>>>

---
title: "Developing Measures of Public Perceptions of Values in Science"
author: |
    | Dan Hicks 
    | Emilio Lobato
    | University of California, Merced
    | [`values-in-science-scale.netlify.app`](https://values-in-science-scale.netlify.app)
toc: false
toc-title: "Overview"
format: 
    revealjs:
        toc-depth: 1
        slide-number: true
        self-contained: true
        theme: [default, theming.scss]
link-citations: true
bibliography: ../paper/VISS.yaml
---

@@

[`values-in-science-scale.netlify.app`](https://values-in-science-scale.netlify.app)
